DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/introduction.tex

\section{Installation}\label{sec_installation}
To work with DOpElib, your need necessarily deal.II, which installation 
we describe first. Afterwards, the DOpElib installation is described and finally
other optional packages might be installed.
\begin{itemize}
\item Install \texttt{deal.II} to your home directory, i.e., it should be located in \\
\texttt{\textasciitilde/deal.II}. \\[1mm]
If you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
Detailed installing instructions for deal.II (here the last version
8.4.0) can be found on 
\texttt{http://www.dealii.org/8.4.0/readme.html}. The deal.II 
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\section{Installation}\label{sec_installation}
To work with DOpElib, your need necessarily deal.II, which installation 
we describe first. Afterwards, the DOpElib installation is described and finally
other optional packages might be installed.
\begin{itemize}
\item Install \texttt{deal.II} to your home directory, i.e., it should be located in \\
\texttt{\textasciitilde/deal.II}. \\[1mm]
If you prefer another position you can install it anywhere but need 
to set the \texttt{DEAL\_II\_DIR} environment variable, so that it 
will be found by cmake, i.e.,
\begin{lstlisting}
export DEAL_II_DIR=[path to deal.ii]
\end{lstlisting}
\begin{remark}
\textbf{Be careful} if you work in several terminal windows and have several deal.II versions. In this case, the
export-command might have to be done again in that new window. Otherwise
another deal.II version might be linked resulting in linker errors or
segmentation faults without useful error message. In order to check to which
deal.II version DOpE is linked, type 
\begin{lstlisting}
echo $DEAL_II_DIR
\end{lstlisting}
in the current terminal window.
\end{remark}
Detailed installing instructions for deal.II (here the last version
8.4.0) can be found on 
\texttt{http://www.dealii.org/8.4.0/readme.html}. The deal.II 
installation instructions are descriptive enough and we omit 
any further comments and refer to their webpage.
%
